Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-06-16 manuscript.tex
minor change

%% Abstract
\begin{abstract}
  This study presents a constrained optimization-based neuro-adaptive control (CONAC) for uncertain Euler-Lagrange systems subject to weight and convex input constraints. 
  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing both types of constraints within a constrained optimization framework.
  The adaptation law of DNN weights is formulated to solve the defined constrained optimization problem, ensuring satisfaction of first-order optimality conditions at steady state.
  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and bounded DNN weights. 
  The proposed controller is validated through a real-time implementation on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
\end{abstract}

@@

More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Lewis:1998aa,Farrell:2006aa}. 
NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) NNs \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep NNs (DNNs) \cite{Patil:2022aa} and their variations. 
Conventionally, SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
However, since DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Griffis:2023aa}, physics-informed NNs (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, and convolutional NNs (CNNs) for learning historical sensor data \cite{Ryu:2024ac}, have further extended the capabilities of neuro-adaptive control systems.
\MSRY{CNN도 넣었습니다.}

@@

The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations. 
The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. 
This problem is exacerbated in neuro-adaptive controllers that attempt to cancel out system dynamics using conventional methods like feedback linearization or backstepping. 
In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs \cite{Khalil:2002aa}.

To address input saturation, many studies introduced auxiliary systems. 
These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. 
For instance, in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly. 
This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.

@@

@@

We consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \rbM\ddq +\rbVm \dq+ \rbF + \rbG + \rbd
    =
    \mysat(\rbu)
    ,
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents the disturbance and $\rbu\in\R^n$ denotes the generalized control input. 
The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)\in\R^{n}$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector, and gravity vector, respectively.
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau\in\R_{>0}$ denotes the maximum norm of control input.

In this study, the saturation function $\mysat(\cdot)$ is assumed to be convex, which is practically common in many engineering systems, since the actuator limits are naturally convex, such as min/max torque limits, and bounds look like a box or ball in the input space.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

@@

The architecture of the proposed CONAC consists of a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN, as illustrated in Fig. \ref{fig:ctrl:diagram}.
Before proceeding to the controller design, some mathematical preliminaries are revisited in Section \ref{sec:sub:math preliminaries}. 
Section \ref{sec:sub:NAC} introduces the neuro-adaptive controller, followed by the DNN model in Section \ref{sec:sub:NN definition}. 
The constrained optimization-based weight adaptation law is presented in Section \ref{sec:adap_laws}.

\begin{figure}[!t]
    \centering
    \includegraphics[width=.99\linewidth]{src/figures/Controller.drawio.pdf}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the proposed constrained optimization-based neuro-adaptive controller (CONAC).}
    \label{fig:ctrl:diagram}
\end{figure}

@@

\begin{propsit}[see, {\cite[Chap. 7, Prop. 7.1.9]{Bernstein:2009aa}}] \label{propsit:kron}
	For a matrix $\mm A\in\R^{n\times m}$ and a vector $\mv b\in\mathbb R^n$, the following property holds:
	\begin{equation}
		\mm A^\top \mv b 
		= 
		\myvec(\mm A^\top\mv b)
		=
		\myvec(\mv b^\top\mm A)
		= 
		(\mm{I}_{m}\otimes \mv b^\top) \myvec(\mm A)
		.
	\end{equation}
\end{propsit}

@@

First, a filtered tracking error $\fe\in\R^n$ is defined as 
\begin{equation}
    \fe := \ddtt{\mv e}+\mm\Lambda \mv e
    ,
    \label{eq:err:filtered}
\end{equation}
where $\mv e := \q - \qd$ denotes the tracking error, $\ddtt{\mv e} := \dq - \dqd$ represents the time derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}_{>0}$ is a user-designed filtering matrix.
Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.

@@

To overcome this issue, a DNN is employed to approximate $\rbu^*$.
Let $\NN:=\NN({\q}_n;\wth): \R^{l_0+1}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where ${\q}_n\in\R^{l_0+1}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
The architecture of DNN $\NN({\q}_n;\wth)$ will be presented in Section \ref{sec:sub:NN definition}, later.
According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, denoted as $\mv g(\cdot)$, with an bounded ideal weight vector $\idealwth\in\R^\Xi$ over a compact subset $\Omega_{n}\in\R^{l_0+1}$ to within $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{n}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
% Furthermore, the theorem states that the norm of $\idealwth$ is bounded such that $\norm{\idealwth}\le \overline\wth<\infty$.
In this study, the ideal weight vector $\idealwth$ is considered a locally optimal solution, rather than a global one.

@@

The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \act_i(\NN_{i-1}), 
        &
        i\in\{1,\dots ,k\},
        \\
        \wV_0^\top {\q}_n,
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i=[w_{ij}]_{i\in\{1,\cdots,l_i+1\},j\in\{1,\cdots,l_{i+1}\}}\in\R^{(l_i+1)\times l_{i+1}}$ and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represent the weight matrix and the activation function of the $i\textsuperscript{th}$ layer, respectively.
The DNN $\NN({\q}_n;\wth)$ has $k+1$ layers, where the input layer is indexed by $i=0$, and the output layer is indexed by $i=k$.
For instance, in Fig.~\ref{fig:DNN}, the DNN $\NN({\q}_n;\wth)$ with $k=2,l_0=2,l_1=l_2=3$, and $l_3=2$ is illustrated.
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$, \ie $l_{k+1}=n$. 
The weights $\wV_i,\forall i\in\{0,\cdots,k\}$ are initialized randomly using uniform distribution at the beginning of the control process.

@@

The adaptation laws for $\estwth$ and $[\lambda_j]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1}, \ie $\min_{\estwth} \max_{[\lambda_j]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda_j]_{j\in\mathcal I})$, as follows:
\begin{subequations}
    \begin{align}
            \ddtt{\estwth}
            &
            =
            -\alpha \pptfrac{L}{\estwth}
            =
            -\alpha 
            \left(
                \pptfrac{J}{\estwth}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq:adap:th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j\pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad \forall j\in\mathcal I,
        \label{eq:adap:lbd}
            \\
            \lambda_j & \leftarrow \max(\lambda_j,0) ,
        \label{eq:adap:lbd:max}
    \end{align}
    \label{eq:adaptation law}%             %%
\end{subequations}
where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L(\cdot)$ and $J(\cdot)$ are suppressed for brevity. 
The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, due to \eqref{eq:adap:lbd:max}. 
When a constraint $c_j$ becomes active, \ie $c_j > 0$, the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation, \ie see, \eqref{eq:adap:lbd}.
Once the violation is resolved and the constraint is no longer active, \ie $c_j \le 0$, the Lagrange multiplier $\lambda_j$ decreases gradually until it returns to zero.
Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max\left(\lambda_j+\tfrac{c_j}{\mu},0\right)$, with $\mu\in\R_{>0}$ being the penalty parameter.

@@

In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ by taking the sign of each entry, \ie
$
    \pptfrac{\fe}{\rbu}
    \approx
    \left[
        \mysign(\pptfrac{r_i}{\tau_j})
    \right]_{i,j\in\{1,\cdots,m\}}
$ 
assuming known control directions.
However, this approach is not applicable to \eqref{eq:sys:filtered}, where control directions are unknown.
Instead, since the sign of the control input matrix is known—owing to the positive definiteness of $\rbM^{-1}$, see, Property \ref{prop:M}—we approximate $\pptfrac{\fe}{\rbu}\approx \mm I_n$.
Consequently, the adaptation law in \eqref{eq:adap:th} becomes:
\begin{equation}
    \ddtt{\estwth}
    \approx
    -\alpha 
    \left(
        \pptfrac{\estNN}
        {\estwth}^\top
        \fe
        +
        \textstyle\sum_{j\in\mathcal{I}}
        \lambda_j 
        \pptfrac{c_j}{\estwth}
    \right)
    .
    \label{eq:adap:th:approx}
\end{equation}

%% ALGORITHM PART; Now omitted!
% The proposed controller is implemented using Algorithm \ref{alg: alg1}. For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$. If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.

% \begin{algorithm}[!t]
%     \caption{Weight Optimizer Implementation.}\label{alg: alg1}
%     \begin{algorithmic}[1]
%         \renewcommand{\algorithmicrequire}{\textbf{Input:}}
%         \renewcommand{\algorithmicensure}{\textbf{Output:}}
%         \REQUIRE $\xi$, $\estwth$, $\lambda_j$, $\eta$
%         \ENSURE  $\estwth$, $\lambda_j$, $\eta$
%         \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
%         \STATE Determine update matrix $\ddtt\eta$ using \eqref{eq. eta dynamics 1};
%         \STATE Update $\eta\leftarrow \eta +\ddtt\eta\cdot T_s$; 
%         \STATE Determine update directions $\ddtt{\estwth}$, $[\ddtt\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
%         \STATE Update weight vector $\estwth\leftarrow \estwth+\ddtt{\estwth}\cdot T_s$;
%         \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\ddtt\lambda_j]_{j\in\mathcal A}\cdot T_s$;
%         \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
%         \STATE Set $\mathcal A \leftarrow \mathcal A - \{j\}$ for all $\lambda_j=0$;
%         \STATE \textbf{RETURN};
%     \end{algorithmic}
%     \label{alg1}
% \end{algorithm}

@@

\begin{remark}
    Assumption \ref{assum:convex} is not restrictive, since, as aforementioned, the control input saturation is practically convex.
    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
\end{remark}

@@

\begin{lem}
    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} hold, then for each active constraint $c_j$, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive; that is $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
    \label{lem:convex:angle}
\end{lem}

@@

Since $\rbu = \estNN$, a linear mapping $\mm T(\cdot):\estwth_k\to\rbu$ that is independent of $\estwth_k$, can be derived using Proposition \ref{propsit:kron}:
\begin{equation}\label{eq:linear:map}
    \begin{aligned}
    \rbu 
    = 
    &
    \estNN 
    % = 
    % \myvec(\estNN)
    =
    \myvec(
        \estwV_k^\top \estact_k
    ) 
    = 
    (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top
    \myvec(\estwV_k)
    \\
    = &
    \underbrace{
        (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top}_{=:\mm T(\estact_k)}
    \estwth_k 
    =
    \mm T(\estact_k) \estwth_k.
    \end{aligned}
\end{equation}
Therefore, the convexity of the input constraints in the $\rbu$-space (see, Assumption \ref{assum:convex}) is preserved in $\estwth_k$-space, implying
that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.

@@

\begin{lem} 
    If control input constraint $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in\{k-1,\cdots, 0\}$, is bounded, provided the norms of $\estwth_i,\ \forall i\in\{k,\cdots, i+1\}$, remain bounded.
    For instance, if $k=2$ and $i=0$, $\norm{\pptfrac{c_j}{\estwth_0}}$ is bounded, provided that $\norm{\estwth_2},\norm{\estwth_1}$ are bounded.
    \MSRY{예시를 넣어봤는데 투머치 일까요?}
    \label{lem:cstr:grad:bound}
\end{lem}

@@

% ------------------------------------
% Controllers: CONAC 
% ------------------------------------
\subsubsection*{Controller 1: \normalfont{(C$_1$)} \textit{CONAC with large update rate, $\beta_j,\forall j\in\mathcal{I}$, of Lagrange Multipliers}}

>>>>

%% Abstract
\begin{abstract}
  This study presents a constrained optimization-based neuro-adaptive control (CONAC) for \color{red}unkown\color{black} Euler-Lagrange systems subject to weight and convex input constraints. 
  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing both types of constraints within a constrained optimization framework.
  The adaptation law of DNN weights is formulated to solve the defined constrained optimization problem, ensuring satisfaction of first-order optimality conditions at steady state.
  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and bounded DNN weights. 
  The proposed controller is validated through a real-time implementation on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
\end{abstract}

@@

More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Lewis:1998aa,Farrell:2006aa}. 
NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Lewis:1996aa,Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) NNs \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep NNs (DNNs) \cite{Patil:2022aa} and their variations. 
Conventionally, SHL and RBF NNs are often employed to approximate \color{red}unkown\color{black} system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
However, since DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Griffis:2023aa}, physics-informed NNs (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, and convolutional NNs (CNNs) for learning historical sensor data \cite{Ryu:2024ac}, have further extended the capabilities of neuro-adaptive control systems.

@@

The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations. 
% The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. 
This issue is exacerbated in neuro-adaptive controllers that utilize NNs as additional control inputs to cancel out uncertain (unknown) system dynamics while conventional model-based control methods, \eg feedback linearization and backstepping, are employed. 
In the cases of feedback linearization and backstepping, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs \cite{Khalil:2002aa}.
Moreover, if the control inputs are already saturated, the NNs are enforced to compensate for the saturated inputs.
In other words, the conventional methods deteriorates the learning process by sabotaging the NN adaptation law, as the feedback error for learning is no longer directly related to the NNs' output.
Hence, the input constraint should be handled in an unity adaptation framework \MSRY{Start from here!}

To address this early discussed issue, many studies introduced auxiliary systems to handle input constraint in adaptation process. 
These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. 
For instance, in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly. 
This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.

@@

This study is extended from our preliminary work presented in \cite{Ryu:2024aa} where the inequality constraint for weight norm was imposed on the neuro-adaptive control design to establish the weight boundedness using constrained optimization framework.
Similar to weight constraints in \cite{Ryu:2024aa}, control input constraints are also incorporated into the CONAC framework to address the convex input saturation problem as well.
Furthermore, the applicability of the proposed CONAC is investigated in a real-time implementation on a 2-DOF robotic manipulator; while the referenced work was limited to the numerical simulation.

@@

We consider an \color{red}unkown\color{black} Euler-Lagrange system modeled as
\begin{equation}
    \rbM\ddq +\rbVm \dq+ \rbF + \rbG + \rbd
    =
    \mysat(\rbu)
    ,
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents the disturbance and $\rbu\in\R^n$ denotes the generalized control input. 
The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)\in\R^{n}$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector, and gravity vector, respectively.
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau\in\R_{>0}$ denotes the maximum norm of control input.

In this study, the saturation function $\mysat(\cdot)$ is assumed to be convex, which is practically common in many engineering systems.
This is because, the actuator limits are naturally convex, such as min/max torque limits, and bounds look like a box or ball in the input space.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

@@

The architecture of the proposed CONAC consists of a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN, as illustrated in Fig. \ref{fig:ctrl:diagram}.
The algorithm of the proposed CONAC is given by Algorithm \ref{alg:CONAC}. 
Before proceeding to the controller design, some mathematical preliminaries are revisited in Section \ref{sec:sub:math preliminaries}. 
Section \ref{sec:sub:NAC} introduces the neuro-adaptive controller, followed by the DNN model in Section \ref{sec:sub:NN definition}. 
The constrained optimization-based weight adaptation law is presented in Section \ref{sec:adap_laws}.

\begin{figure}[!t]
    \centering
    \includegraphics[width=.999\linewidth]{src/figures/Controller.drawio.pdf}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the proposed constrained optimization-based neuro-adaptive controller (CONAC).}
    \label{fig:ctrl:diagram}
\end{figure}

\begin{algorithm}[!t]
    \caption{Proposed CONAC Algorithm}\label{alg:CONAC}
    \begin{algorithmic}[1]
        \STATE \textbf{Initialize:} DNN weights $\estwth$ and Lagrange multipliers $\lambda_j$
        \FOR{each sampling time}
            \STATE Measure current state $\q,\dq$
            \STATE Compute filtered error $\fe$ \eqref{eq:err:filtered}
            \STATE Update DNN weights $\estwth$ using $\fe$ \eqref{eq:adap:th}
            \STATE Update Lagrange multipliers $\lambda_j$ based on constraint function $c_j$ \eqref{eq:adap:lbd} and \eqref{eq:adap:lbd:max}
            \STATE Compute control input $\rbu$ (DNN output) \eqref{eq:control:est} and \eqref{eq:DNN:architecture}
            \STATE Apply control input $\rbu$ to the system \eqref{eq:sys1}
        \ENDFOR
    \end{algorithmic}
\end{algorithm}

@@

\begin{propsit}[see {\cite[Chap. 7, Prop. 7.1.9]{Bernstein:2009aa}}] \label{propsit:kron}
	For a matrix $\mm A\in\R^{n\times m}$ and a vector $\mv b\in\mathbb R^n$, the following property holds:
	\begin{equation}
		\mm A^\top \mv b 
		= 
		\myvec(\mm A^\top\mv b)
		=
		\myvec(\mv b^\top\mm A)
		= 
		(\mm{I}_{m}\otimes \mv b^\top) \myvec(\mm A)
		.
	\end{equation}
\end{propsit}

@@

Given that the Euler-Lagrange system \eqref{eq:sys1} exhibits second-order dynamics, a filtered error $\fe\in\R^n$ is introduced to convert the system into a first-order system, as follows:
\begin{equation}
    \fe := \ddtt{\mv e}+\mm\Lambda \mv e
    ,
    \label{eq:err:filtered}
\end{equation}
where $\mv e := \q - \qd$ denotes the tracking error, $\ddtt{\mv e} := \dq - \dqd$ represents the time derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}_{>0}$ is a user-designed filtering matrix.
Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.

@@

To overcome this issue, a DNN is employed to approximate $\rbu^*$.
Let $\NN:=\NN({\q}_n;\wth): \R^{l_0+1}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where ${\q}_n\in\R^{l_0+1}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
The architecture of DNN $\NN({\q}_n;\wth)$ will be presented in Section \ref{sec:sub:NN definition}, later.
According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, denoted as $\mv g(\cdot)$, with an ideal weight vector $\idealwth\in\R^\Xi$ over a compact subset $\Omega_{n}\in\R^{l_0+1}$ to within $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{n}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
% Furthermore, the theorem states that the norm of $\idealwth$ is bounded such that $\norm{\idealwth}\le \overline\wth<\infty$.
In this study, the ideal weight vector $\idealwth$ is assumed to be bounded by Assumption \ref{assum:feasible} and \cite[Assum. 1]{Lewis:1996aa}, and considered a locally optimal solution, rather than a global one.

@@

The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented from the $0\textsuperscript{th}$ input layer to the $k\textsuperscript{th}$ output layer, as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \act_i(\NN_{i-1}), 
        &
        i\in\{1,\dots ,k\},
        \\
        \wV_0^\top {\q}_n,
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i=[w_{ij}]_{i\in\{1,\cdots,l_i+1\},j\in\{1,\cdots,l_{i+1}\}}\in\R^{(l_i+1)\times l_{i+1}}$ and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represent the weight matrix and the activation function of the $i\textsuperscript{th}$ layer, respectively.
The DNN $\NN({\q}_n;\wth)$ has $k+1$ layers, where the input layer is indexed by $i=0$, and the output layer is indexed by $i=k$.
For instance, in Fig.~\ref{fig:DNN}, the DNN $\NN({\q}_n;\wth)$ with $k=2,l_0=2,l_1=l_2=3$, and $l_3=2$ is illustrated.
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$, \ie $l_{k+1}=n$. 
The weights $\wV_i,\forall i\in\{0,\cdots,k\}$ are initialized randomly using uniform distribution at the beginning of the control process.

@@

The adaptation laws for $\estwth$ and $[\lambda_j]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1}, \ie $\min_{\estwth} \max_{[\lambda_j]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda_j]_{j\in\mathcal I})$, as follows:
\begin{subequations}
    \begin{align}
            \ddtt{\estwth}
            &
            =
            -\alpha \pptfrac{L}{\estwth}
            =
            -\alpha 
            \left(
                \pptfrac{J}{\estwth}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq:adap:th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j\pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad \forall j\in\mathcal I,
        \label{eq:adap:lbd}
            \\
            \lambda_j & \leftarrow \max(\lambda_j,0) ,
        \label{eq:adap:lbd:max}
    \end{align}
    \label{eq:adaptation law}%             %%
\end{subequations}
where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L(\cdot)$ and $J(\cdot)$ are suppressed for brevity. 
The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, due to \eqref{eq:adap:lbd:max}. 
When a constraint $c_j$ becomes active, \ie $c_j > 0$, the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation, \ie see \eqref{eq:adap:lbd}.
Once the violation is resolved and the constraint is no longer active, \ie $c_j \le 0$, the Lagrange multiplier $\lambda_j$ decreases gradually until it returns to zero.
Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max\left(\lambda_j+\tfrac{c_j}{\mu},0\right)$, with $\mu\in\R_{>0}$ being the penalty parameter.

@@

In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ by taking the sign of each entry, \ie
$
    \pptfrac{\fe}{\rbu}
    \approx
    \left[
        \mysign(\pptfrac{r_i}{\tau_j})
    \right]_{i,j\in\{1,\cdots,m\}}
$ 
assuming known control directions.
However, this approach is not applicable to \eqref{eq:sys:filtered}, where control directions are unknown.
Instead, since the sign of the control input matrix is known—owing to the positive definiteness of $\rbM^{-1}$, see Property \ref{prop:M}—we approximate $\pptfrac{\fe}{\rbu}\approx \mm I_n$.
Consequently, the adaptation law in \eqref{eq:adap:th} becomes:
\begin{equation}
    \ddtt{\estwth}
    \approx
    -\alpha 
    \left(
        \pptfrac{\estNN}
        {\estwth}^\top
        \fe
        +
        \textstyle\sum_{j\in\mathcal{I}}
        \lambda_j 
        \pptfrac{c_j}{\estwth}
    \right)
    .
    \label{eq:adap:th:approx}
\end{equation}

@@

\begin{remark}
    Assumption \ref{assum:convex} is not restrictive, since, as aforementioned, the control input saturation is practically convex.
    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
    This assumption will be used in the stability analysis (see Lemma \ref{lem:convex:angle}).
\end{remark}

@@

\begin{lem}
    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} hold, then for each active constraint $c_j$, the angle between the output layer's weight vector $\estwth_k$ and $\pptfrac{c_j}{\estwth_k}$ is positive; that is $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
    \label{lem:convex:angle}
\end{lem}

@@

Since $\rbu = \estNN$, a linear mapping $\mm T(\cdot):\estwth_k\to\rbu$ that is independent of $\estwth_k$, can be derived using Proposition \ref{propsit:kron}:
\begin{equation}\label{eq:linear:map}
    \begin{aligned}
    \rbu 
    = 
    &
    \estNN 
    % = 
    % \myvec(\estNN)
    =
    \myvec(
        \estwV_k^\top \estact_k
    ) 
    = 
    (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top
    \myvec(\estwV_k)
    \\
    = &
    \underbrace{
        (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top}_{=:\mm T(\estact_k)}
    \estwth_k 
    =
    \mm T(\estact_k) \estwth_k.
    \end{aligned}
\end{equation}
Therefore, the convexity of the input constraints in the $\rbu$-space (see Assumption \ref{assum:convex}) is preserved in $\estwth_k$-space, implying
that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.

@@

\begin{lem} 
    If control input constraint $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in\{k-1,\cdots, 0\}$, is bounded, provided the norms of $\estwth_i,\ \forall i\in\{k,\cdots, i+1\}$, remain bounded.
    \label{lem:cstr:grad:bound}
\end{lem}

For instance, if $k=3$ and $i=1$, $\norm{\pptfrac{c_j}{\estwth_1}}$ is bounded, provided that $\norm{\estwth_3},\norm{\estwth_2}$ are bounded.

@@

% ------------------------------------
% Controllers: CONAC with large beta 
% ------------------------------------
\subsubsection*{Controller 1: \normalfont{(C$_1$)} \textit{CONAC with large update rate, $\beta_j,\forall j\in\mathcal{I}$, of Lagrange Multipliers}}
